Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-01 paper/main.tex

\author{
Adler Perotte\hspace{1cm} Nicholas Bartlett \hspace{1cm} Noemie Elhadad \hspace{1cm} Frank Wood\\
Columbia University, New York, NY 10027, USA \\
\texttt{\{ajp9009@dbmi,bartlett@stat,noemie@dbmi,fwood@stat\}.columbia.edu}
%\texttt{pfau@neurotheory.columbia.edu} 
%\texttt{\{bartlett,fwood\}@stat.columbia.edu} 
}

>>>>

\author{
Adler Perotte\hspace{1cm} Nicholas Bartlett \hspace{1cm} No\'emie Elhadad \hspace{1cm} Frank Wood\\
Columbia University, New York, NY 10027, USA \\
\texttt{\{ajp9009@dbmi,bartlett@stat,noemie@dbmi,fwood@stat\}.columbia.edu}
%\texttt{pfau@neurotheory.columbia.edu} 
%\texttt{\{bartlett,fwood\}@stat.columbia.edu} 
}
